Autonomous Realization of Simple Machines

### 2014-05-23 doc/paper/paper.tex
Added manip picture

The primary locomotion strategy for Golem Krang is to balance on its two wheels, keeping its
center of mass on the vertical plane through its wheel axis. Modeled as an inverted pendulum,
locomotion via balancing has a few advantages over running on both the wheels and the back caster of
the robot. First, the footprint of the robot is smaller, 54 cm front to back due to diameter
of the wheels while dynamically balancing as opposed to 86 cm when the robot is staticly grounded.
Second, the locomotion of the robot is simpler to model since the fixed caster without omnidirectional
wheels has different friction properties as the robot spins, moves forward and backward.

@@

% Why balance?
% How to balance? 
% How to balance while carrying objects?

>>>>

The primary locomotion strategy for Golem Krang is to balance on its two wheels, keeping its
center of mass on the vertical plane through its wheel axis. Modeled as an inverted pendulum,
locomotion via balancing has a few advantages over running on both the wheels and the back caster of
the robot. First, the footprint of the robot is smaller, 54 cm front to back due to diameter
of the wheels while dynamically balancing, as opposed to 86 cm when the robot is staticly grounded.
Second, the locomotion of the robot is simpler to model since the fixed caster without omnidirectional
wheels has different ground friction properties as the robot spins, moves forward and backward.

@@

\begin{figure}[ht!] 
  \centering
  \includegraphics[width=1.0\linewidth]{Figures/manipulation.png}
  \caption{.}
  \label{fig:manipulation}
\end{figure}

asdf
